\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{textcomp}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r} \\
  \textbf{\href{http://oscarnord.com/}{\huge Oscar Nord}}  \\ \\
  \href{http://oscarnord.com/}{http://www.oscarnord.com} & Email : \href{mailto:oscar.nord@gmail.com}{oscar.nord@gmail.com} \\
  \href{http://github.com/furbee/}{http://github.com/furbee} & Mobile : +46(0)72-7320801 \\
  \href{http://linkedin.com/in/oscarnord/}{http://linkedin.com/in/oscarnord/} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Institute of Technology at Linköping University}{Norrköping, Sweden}
      {Master of Science in Media Technology and Engineering}
      {Aug. 2017 -- Present}
    \resumeSubheading
      {The Institute of Technology at Linköping University}{Norrköping, Sweden}
      {Bachelor of Science in Media Technology and Engineering} 
      {Aug. 2013 -- June. 2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FA Works}{Stockholm, Sweden}
      {Visual / Interactive Artist}{July 2017 - Present}
      \resumeItemListStart
        \resumeItem{Interactive Artist}
          {Responsible for interactive solutions, such as VR and interactive applications. Developing VR/AR Applications using Unity and Google Daydream. The application visualizes apartments and houses using HTC Vive/Oculus Rift and smartphones (Google Cardboard etc.).}
      \resumeItemListEnd
      
    \resumeSubheading
      {Freelancer}{Norrköping, Sweden}
      {3D-Artist} {Jan 2014 - July 2016}
      \resumeItemListStart
        \resumeItem{FX/technical Artist for Origin Unknown (Parkgate Entertainment)}
          {Created particle-effects and complex simulations using Houdini and Python.}
        \resumeItem{3D Artist for Gustavsvik Lost City (TV advertisement)}
          {Work includes 3D-modeling, texturing and rendering.}
        \resumeItem{3D Artist for Örebro Race Day (Online advertisement)}
          {Work includes 3D-modeling, texturing, animation, photography and rendering.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects Source available on GitHub}
  \resumeSubHeadingListStart
    \resumeSubItem{\textmu{}TUI \textit{(C++)} }
      { \\
      \indent-- Bachelor project for Visualization Center C in Norrköping, Sweden. \\
      \indent-- TUI (Tangible User Interface) application for navigating information on a large touch screen with physical cards.\\
      \indent-- Responsible for the image processing of the project.\\
      \indent-- Used OpenCV and ArUco to identify and find the positioning of the card in real-time.\\}
      
    \resumeSubItem{Transcension3D \textit{(C++)} }
      { \\ 
      \indent-- 3D game engine written in C++ using OpenGL 3.3. \\
      \indent-- Engine uses Blender for level editing and Assimp for scene loading. \\
      \indent-- The core architecture of the engine is built around the Entity-Component-System pattern (EntityX). \\
      \indent-- Continuous physics simulation and collision detection is handled by Bullet Physics Library.}
      
      \resumeSubItem{FoundIt, East Sweden Hack 2017 hackathon project \textbf{(start date: 2017-09-08)} \textit{Swift, JavaScript}}
      { \\ 
      \indent-- NFC tags from Thin Film Electronics to be used for finding lost items.\\
      \indent-- 46elks API to be used for notifying the user with SMS and Senion API for indoor positioning.\\
      \indent-- OpenStreetMap will be used as open data.\\
      \indent-- Web server and an app will be developed for the user.\\
      }
      
    \resumeSubItem{Fluids \textit{(C++)} }
       {\\ 
       \indent-- Fluid simulation using the \textit{Navier-Stokes}-equations done in the course TNM085, Modeling project.}

  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership Experience}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming mentor, LiTHehack 17/18}
      {\\
      \indent-- LiTHehack is a student-driven project at Linköping University aiming to help and inspire students with programming. \\
      \indent-- Available 4 hours every week and offer guidance in everything from web programming to C++.\\
      \indent-- Holding lectures about diverse programming related topics such as Git.\\}
      
    \resumeSubHeadingListEnd
  
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C++, Python, C\#, JavaScript, MATLAB, Java}
      \hfill
      \textbf{Technologies}{: OpenGL, OpenCV, Git}
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
